Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2020-11-16 paper/main.tex
Some fixes from MBN comments

The widely used mixing-length theory of convection, parametrised by $\mlt$, has been tested throughout the Hertzspring-Russell diagram with 3D hydrodynamical simulations \citep{Trampedach.Stein.ea2014, Magic.Weiss.ea2015} and asteroseismology \citep{Tayar.Somers.ea2017, Viani.Basu.ea2018, Li.Bedding.ea2018} with values in the range $0.8 \lesssim \mlt/\alpha_{\mathrm{MLT}, \odot} \lesssim 1.2$ where $\alpha_{\mathrm{MLT}, \odot}$ is the value calibrated to the Sun. However, in many grids of stellar models, a constant value calibrated to reproduce the Sun is assumed. This can lead to systematic uncertainties in stellar ages due to the effects of variable mixing depending on the mixing length. In this work, we experiment with two prior assumptions for $\mlt$, one assuming the best-fitting $\mlt$ is normally distributed in our sample, and the other assuming it is constant throughout.

Our HBM requires a way to map from the stellar initial (or bulk) properties to predict observables. We can achieve this with a large grid of stellar evolutionary models. However, a discrete grid can produce inaccurate posterior distributions, limited to the grid resolution. Increasing the resolution is computationally demanding, especially when scaling to higher input dimensions. One solution is to interpolate the stellar models, as is common in the isochrone-fitting method \citep[see e.g.][]{Berger.Huber.ea2020}. However, interpolation can become computationally expensive at high input dimensions and grid size, and evaluating the likelihood using modern Bayesian sampling techniques is slow. Instead, we use machine learning to map stellar model inputs to observables to provide a fast way to sample the HBM. In this work, we train an artificial neural network (ANN) on a large grid of stellar models. There have been similar applications of ANNs in asteroseismology \citep{Verma.Hanasoge.ea2016, Hendriks.Aerts2019} but not yet in the context of an HBM. Using the machine learning speed-up, we demonstrate a scalable method for obtaining fundamental stellar parameters.

@@

In Section \ref{sec:ann}, we describe a method to replace the grid of stellar models with a smooth function approximation. We trained an ANN on the grid of stellar models to map input parameters to output observables. Fast evaluation of the ANN gradient is required during training. Consequently, estimating the gradient of the model likelihood is possible with an ANN. Hence, we open up the possibility of using a Hamiltonian Monte Carlo (HMC) algorithm which requires the gradient to sample the model posterior -- for example, using the No-U-Turn Sampler \citep[NUTS;][]{Hoffman.Gelman2014}.

@@

We chose to ignore the well known, yet poorly characterised impact of modelled oscillation mode inaccuracies in the near-surface region of the star \citep{Kjeldsen.Bedding.ea2008, Ball.Gizon2014, Sonoi.Samadi.ea2015}. This typically presents only a small effect when considering the average large frequency spacing, $\dnu$. % This may need more

@@

In this work, we considered a fully-connected ANN, where each neuron in layer $j-1$ is connected to every neuron in layer $j$. The output of the $k$-th neuron in layer $j$ is, 
%
\begin{equation}
    x_{j, k}=f_j(\boldsymbol{w}_{j, k} \cdot \boldsymbol{x}_{j-1} + b_{j, k})
\end{equation}
%
where $f_j$ is the \emph{activation} function for the $j$-th layer, $\boldsymbol{w}_{j, k}$ are the weights connecting all the neurons in layer $j-1$ to the current neuron, and $b_{j, k}$ is the bias. This generalises such that the output of the $j$-th layer is,
%
\begin{equation}
    \boldsymbol{x}_{j}=f_j(\boldsymbol{W}_{j} \cdot \boldsymbol{x}_{j-1} + \boldsymbol{b}_{j}),
\end{equation}
%
where $\boldsymbol{W}_j$ is the matrix of weights leading to all neurons in the $j$-th layer. For a regression ANN, we typically have a linear activation function applied to the output of the final layer. Therefore, the output of a network of $H$ hidden layers with initial input $\boldsymbol{\mathbb{X}}$ is,
%
\begin{equation}
    \widetilde{\boldsymbol{\mathbb{Y}}} = \boldsymbol{W}_{H} \cdot f_{H-1}(\dots f_1(\boldsymbol{W}_1 \cdot f_0(\boldsymbol{W}_{0} \cdot \boldsymbol{\mathbb{X}} + \boldsymbol{b}_{0}) + \boldsymbol{b}_1) ) + \boldsymbol{b}_{H}
\end{equation}
%
We also restricted our configuration to an ANN with the same number of neurons, $N$ in each hidden layer. Hereafter, we refer to our choice of neurons per layer, $N$ and hidden layers, $H$ as the \emph{architecture}.

@@

We needed to train an ANN which would reproduce stellar observables according to our choice of physics with greater accuracy than typical observational precisions. We experimented with a variety of ANN parameter choices, such as the architecture, activation function, optimization algorithm and loss function. We tuned the ANN parameters by varying them in both a grid-based and heuristic approach, each time evaluating the accuracy using the test dataset.

During initial tuning, we found that having stellar age as an input was unstable, because it varied heavily with the other input parameters. We mitigated this by introducing an input to describe the fraction of time a star had spent in a given evolutionary phase, $f_\mathrm{evol}$. 
%
\begin{equation}
    f_\mathrm{evol} = \begin{cases}
        f_\mathrm{MS},\quad &f_\mathrm{MS} \leq 1\\
        1 + \frac{\tau\,-\,\tau_\mathrm{MS}}{\tau_\mathrm{end}\,-\,\tau_\mathrm{MS}},\quad &f_\mathrm{MS} > 1
    \end{cases}
\end{equation}
%
where $\tau_\mathrm{end}$ is the age of the star at the end of the track,
%
\begin{equation}
    f_\mathrm{MS} = \frac{\tau}{\tau_\mathrm{MS}},
\end{equation}
%
and $\tau_\mathrm{MS}$ is the MS lifetime. In other words, a star with $f_\mathrm{evol} \in (0, 1]$ is in its MS phase, burning hydrogen in its core, and $f_\mathrm{evol} \in (1, 2]$ has left the MS. Consequently, $f_\mathrm{evol}$ gives the ANN information about the internal state of the star which affects the output observables. Otherwise, $f_\mathrm{evol}$ is a meaningless parameter, although it could loosely be interpreted as a measure of the evolutionary phase of the star.

We also observed that the ANN struggled to fit areas with a high rate of change in observables, partly because of poor grid coverage. To bias training to such areas, we calculated the gradient in $\teff$ and $\log g$ between each point for each stellar evolutionary track and used them as optional weights to the loss during tuning. These weights multiplied the difference between the ANN prediction and the training data in our chosen loss function.

@@

We standardised the training dataset by subtracting the median, $\mu_{1/2}$ and dividing by the standard deviation, $\sigma$ for each input and output parameter. We found that the ANN performed better when the training data was scaled in this way. In Table \ref{tab:std}, we show the locations and scales of the standardisation for our chosen input and output parameters.

@@

We devised three Bayesian models, each with varying levels of parameter sharing (pooling) between stars in the population. Initially, we tested the models and demonstrated reduction of statistical uncertainties in the stellar fundamental parameters by analysing a random sample of 100 synthetic stars modelled using MESA. Then, we applied the models to the sample of stars in Table \ref{tab:data} (with and without Solar data for two of the models) and compared the results with that of \citetalias{Serenelli.Johnson.ea2017}.

@@

We chose weakly-informative, bounded priors for the independent parameters, restricting them to their respective ranges in the ANN training data. Although the neural network is able to make predictions outside the training data range, these have not been tested and may be unreliable. Therefore, we used a beta distribution with $\alpha = \beta = 1.2$ as the prior PDF on the independent parameters, transformed such that the probability is null outside the chosen range,
%
\begin{align}
    p(\boldsymbol{\theta}_i) &\propto \prod_{k=1}^{N_{\theta}} \mathcal{B}\left(\tilde{\theta}_{k, i} | 1.2, 1.2\right),\\
    \tilde{\theta}_{k, i} &= \frac{\theta_{k, i} - \theta_{k, \mathrm{min}}}{\theta_{k, \mathrm{max}} - \theta_{k, \mathrm{min}}},
\end{align}
%
where the beta distribution is defined as,
%
\begin{equation}
    \mathcal{B}(x | \alpha, \beta) = \frac{x^{\,\alpha-1}(1-x)^{\,\beta-1}}{\int_{0}^{1} u^{\,\alpha-1}(1-u)^{\,\beta-1} \mathrm{d} u}.
\end{equation}
%
The beta distribution was preferred over a bounded uniform distribution because our sampler evaluates the gradient of the posterior and hence sensitive to discontinuities.

Using notation which represents some random variable $x \sim q$ as equivalent to being drawn from some probability distribution $p(x) \propto q(x)$ where $q(x)$ is a non-normalised probability density function, we write the priors for $\boldsymbol{\theta}_i$ as,
%
\begin{align*}
    f_{\mathrm{evol}, i} &\sim 0.01 + 1.99 \cdot \mathcal{B}(1.2, 1.2),\\
    M_i &\sim 0.8 + 0.4 \cdot \mathcal{B}(1.2, 1.2),\\
    \alpha_{\mathrm{MLT}, i} &\sim 1.5 + \mathcal{B}(1.2, 1.2),\\
    Y_{\mathrm{init}, i} &\sim 0.24 + 0.08 \cdot \mathcal{B}(1.2, 1.2),\\
    Z_{\mathrm{init}, i} &\sim 0.005 + 0.035 \cdot \mathcal{B}(1.2, 1.2),\\
\end{align*}
%
where each beta distribution is scaled to cover the boundaries of the grid of stellar models computed in Section \ref{sec:grid}.

We made predictions for each star using the trained ANN, $\{\log(\tau)_i, T_{\mathrm{eff}, i}, R_i, \dnu_i, \metallicity_{\mathrm{surf}, i}\} = \boldsymbol{f}_{\mathrm{ANN}}(\boldsymbol{\theta}_i)$, from which we derived the luminosity, $L_i$ using the Stefan-Boltzmann law. Out of the model parameters, those which may be observed are denoted by ${\boldsymbol{\mu}}_{i} = {\boldsymbol{f}}(\boldsymbol{\theta}_i)$. Thus, we write the likelihood we observe any $\boldsymbol{d}_i$ with known uncertainty, $\boldsymbol{\sigma}_{i}$ given the model as,
%
\begin{equation}
    p(\boldsymbol{d}_i | \boldsymbol{\theta}_i) = \prod_{k=1}^{N_\mathrm{obs}} \frac{1}{\sigma_{k, i} \sqrt{2\pi}} \exp\left[ - \frac{(d_{k, i} - \mu_{k, i})^2}{2 \sigma_{k, i}^2} \right],
    \label{eq:like}
\end{equation}
%
where $N_\mathrm{obs}$ is the number of observed variables. We chose to use observed $\teff$, $L$, $\dnu$ and $\metallicity$ collated for our sample as described in Section \ref{sec:data}.

@@

Similarly, for the second term of Equation \ref{eq:ppool}, we chose to partially-pool the mixing-length parameter. We assume that convection in stars of a similar mass, evolutionary stage and area of the HR diagram may be approximated using a similar value of $\mlt$, but the accuracy of the mixing-length theory may vary from star-to-star. There is theoretical evidence for such a variation with $\metallicity$, $\teff$ and $\log{g}$ in 3D hydrodynamical stellar models \citep{Magic.Weiss.ea2015,Viani.Basu.ea2018}. However, investigating such dependencies are beyond this scope of this paper. Given the small range of our sample, any such variation will be absorbed by the spread parameter, $\sigma_\alpha$. Therefore, we decided to describe the prior on $\boldsymbol{\alpha}_\mathrm{MLT}$ as,
%
\begin{equation}
    p(\boldsymbol{\alpha}_{\mathrm{MLT}} | \mu_\alpha, \sigma_\alpha) = \prod_{i=1}^{N_\mathrm{stars}} \mathcal{N}({\alpha}_{\mathrm{MLT}, i} | \mu_\alpha, \sigma_\alpha)
\end{equation}
%

@@

We built another hierarchical model similar to the PP model except that $\mlt$ is max-pooled. In other words, we assumed that the mixing length must be the same value for every star in the sample, but still allowed it to freely vary. Thus the hyperparameters are now, $\boldsymbol{\phi} = \{\Delta Y/\Delta Z, Y_P, \sigma_Y, \mlt\}$. The posterior distribution of the model takes the same form as in Equation \ref{eq:hbmbayes} except that the mixing-length theory parameter for the $i$-th star is,
%
\begin{equation}
    \alpha_{\mathrm{MLT}, i} = \mlt,
\end{equation}
%
where,
\begin{equation}
    \mlt \sim 1.5 + \mathcal{B}(1.2, 1.2).
\end{equation}
% %
% \begin{equation}
%     p(\boldsymbol{\alpha}_\mathrm{MLT} | \mlt) = \prod_{i=1}^{N_\mathrm{stars}} \delta (\alpha_{\mathrm{MLT}, i} | \mlt)
% \end{equation}
% %
% where $\delta(x | \alpha)$ is defined as,
% %
% \begin{equation}
%     \delta(x | \alpha) = \begin{cases}
%         + \infty, &\quad x = \alpha\\
%         0, &\quad x \neq \alpha
%     \end{cases}
% \end{equation}
chosen such that $\mlt$ is confined to the boundaries of the grid of stellar models ($1.5 < \mlt < 2.5$). In other words, $\mlt$ is a free parameter in the model but is assumed to be the same in all stars.

@@

% \subsection{The APOKASC sample}\label{sec:apk-results}

In this section, we present the results for each of the NP, PP and MP models ran with the sample of 81 APOKASC dwarfs and subgiants as inputs. We also present the results for the PPS and MPS models ran with Solar data as a calibrator. Firstly, we show the reduction in age, mass and radius uncertainty with the addition of pooling in Section \ref{sec:param-results}. We then show the results for model hyperparameters in Section \ref{sec:hparam-results} where we infer the initial helium abundance and mixing-length parameter distribution in the sample.

@@

\section{Training the ANN}

>>>>

The widely used mixing-length theory of convection, parametrised by $\mlt$, has been tested throughout the Hertzsprung-Russell diagram with 3D hydrodynamical simulations \citep{Trampedach.Stein.ea2014, Magic.Weiss.ea2015} and asteroseismology \citep{Tayar.Somers.ea2017, Viani.Basu.ea2018, Li.Bedding.ea2018} with values in the range $0.8 \lesssim \mlt/\alpha_{\mathrm{MLT}, \odot} \lesssim 1.2$ where $\alpha_{\mathrm{MLT}, \odot}$ is the value calibrated to the Sun. However, in many grids of stellar models, a constant value calibrated to reproduce the Sun is assumed. This can lead to systematic uncertainties in stellar ages due to the effects of variable mixing depending on the mixing length. In this work, we experiment with two prior assumptions for $\mlt$, one assuming the best-fitting $\mlt$ is normally distributed in our sample, and the other assuming it is constant throughout.

Our HBM requires a way to map from the stellar initial (or bulk) properties to predict observables. We can achieve this with a large grid of stellar evolutionary models. However, a discrete grid can produce inaccurate posterior distributions, limited to the grid resolution. Increasing the resolution is computationally demanding, especially when scaling to higher input dimensions. One solution is to interpolate the stellar models, as is common in the isochrone-fitting method \citep[see e.g.][]{Berger.Huber.ea2020}. However, interpolation can become computationally expensive at high input dimensions and grid size, and evaluating the likelihood using modern Bayesian sampling techniques is slow. Therefore, we use machine learning to map stellar model inputs to observables to provide a fast way to sample the HBM. In this work, we train an artificial neural network (ANN) on a large grid of stellar models. There have been similar applications of ANNs in asteroseismology \citep{Verma.Hanasoge.ea2016, Hendriks.Aerts2019} but not yet in the context of an HBM. Using the machine learning speed-up, we demonstrate a scalable method for obtaining fundamental stellar parameters.

@@

In Section \ref{sec:ann}, we describe a method to replace the grid of stellar models with a smooth function approximation. We trained an ANN on the grid of stellar models to map input parameters to output observables. Evaluation of the ANN gradient is required during training. Consequently, estimating the gradient of the model likelihood is fast and simple when the observables are generated by an ANN. Hence, we open up the possibility of using a Hamiltonian Monte Carlo (HMC) algorithm which requires the gradient to sample the model posterior -- for example, using the No-U-Turn Sampler \citep[NUTS;][]{Hoffman.Gelman2014}.

@@

We chose to ignore the well known, yet poorly characterised impact of modelled oscillation mode inaccuracies in the near-surface region of the star \citep{Kjeldsen.Bedding.ea2008, Ball.Gizon2014, Sonoi.Samadi.ea2015}. This typically presents only a small effect compared to observational uncertainties when considering the average large frequency spacing, $\dnu$. A thorough treatment of systematics related to $\dnu$ is instead left to future work. % This may need more

@@

In this work, we considered a fully-connected ANN, where each neuron in layer $j-1$ is connected to every neuron in layer $j$. The output of the $k$-th neuron in layer $j$ is, 
%
\begin{equation}
    x_{j, k}=f_j(\boldsymbol{w}_{j, k} \cdot \boldsymbol{x}_{j-1} + b_{j, k})
\end{equation}
%
where $f_j$ is the \emph{activation} function for the $j$-th layer, $\boldsymbol{w}_{j, k}$ are the weights connecting all the neurons in layer $j-1$ to the current neuron, and $b_{j, k}$ is the bias. This generalises such that the output of the $j$-th layer is,
%
\begin{equation}
    \boldsymbol{x}_{j}=f_j(\boldsymbol{W}_{j} \cdot \boldsymbol{x}_{j-1} + \boldsymbol{b}_{j}),
\end{equation}
%
where $\boldsymbol{W}_j$ is the matrix of weights leading to all neurons in the $j$-th layer. For a regression ANN, we typically have a linear activation function applied to the final output layer. Layers of neurons between the input and output layers are called \emph{hidden} layers. Therefore, the output of a network of $H$ hidden layers with initial input $\boldsymbol{\mathbb{X}}$ is,
%
\begin{equation}
    \widetilde{\boldsymbol{\mathbb{Y}}} = \boldsymbol{W}_{H} \cdot f_{H-1}(\dots f_1(\boldsymbol{W}_1 \cdot f_0(\boldsymbol{W}_{0} \cdot \boldsymbol{\mathbb{X}} + \boldsymbol{b}_{0}) + \boldsymbol{b}_1) ) + \boldsymbol{b}_{H}
\end{equation}
%
We also restricted our configuration to an ANN with the same number of neurons, $N$ in each hidden layer. Hereafter, we refer to our choice of neurons per layer, $N$ and hidden layers, $H$ as the \emph{architecture} (see Figure \ref{fig:net}).

@@

We trained an ANN to reproduce stellar observables according to our choice of physics with greater accuracy than typical observational precisions. We experimented with a variety of ANN parameter choices, such as the architecture, activation function, optimization algorithm and loss function. We tuned the ANN parameters by varying them in both a grid-based and heuristic approach, each time evaluating the accuracy using the test dataset.

During initial tuning, we found that having stellar age as an input was unstable, because it varied heavily with the other input parameters. We mitigated this by introducing an input to describe the fraction of time a star had spent in a given evolutionary phase, $f_\mathrm{evol}$. 
%
\begin{equation}
    f_\mathrm{evol} = \begin{cases}
        f_\mathrm{MS},\quad &f_\mathrm{MS} \leq 1\\
        1 + \frac{\tau\,-\,\tau_\mathrm{MS}}{\tau_\mathrm{end}\,-\,\tau_\mathrm{MS}},\quad &f_\mathrm{MS} > 1
    \end{cases}
\end{equation}
%
where $\tau_\mathrm{end}$ is the age of the star at the end of the track,
%
\begin{equation}
    f_\mathrm{MS} = \frac{\tau}{\tau_\mathrm{MS}},
\end{equation}
%
and $\tau_\mathrm{MS}$ is the MS lifetime. A star with $f_\mathrm{evol} \in (0, 1]$ is in its MS phase, burning hydrogen in its core, and $f_\mathrm{evol} \in (1, 2]$ has left the MS. Consequently, $f_\mathrm{evol}$ gives the ANN information about the internal state of the star which affects the output observables. Otherwise, $f_\mathrm{evol}$ has little physical meaning, although it could be interpreted as a measure of the evolutionary phase of the star.

We also observed that the ANN trained poorly in areas with a high rate of change in observables, likely because of poor grid coverage in those areas. To bias training to such areas, we calculated the gradient in $\teff$ and $\log g$ between each point for each stellar evolutionary track and used them as optional weights to the loss during tuning. These weights multiplied the difference between the ANN prediction and the training data in our chosen loss function.

@@

We standardised the training dataset by subtracting the median, $\mu_{1/2}$ and dividing by the standard deviation, $\sigma$ for each input and output parameter. We found that the ANN performed better when the training data was scaled in this way as opposed to no scaling at all. In Table \ref{tab:std} of Appendix \ref{sec:apx-train} we show the locations and scales of the standardisation for our chosen input and output parameters.

@@

We devised three Bayesian models, each with varying levels of parameter sharing (pooling) between stars in the population. Initially, we tested the models and demonstrated reduction of statistical uncertainties in the stellar fundamental parameters by analysing a random sample of 100 synthetic stars modelled using MESA. Then, we applied the models to the sample of stars in Table \ref{tab:data} (with and without solar data for two of the models) and compared the results with that of \citetalias{Serenelli.Johnson.ea2017}.

@@

We chose weakly-informative, bounded priors for the independent parameters, restricting them to their respective ranges in the ANN training data. Although the neural network is able to make predictions outside the training data range, these have not been tested and may be unreliable. Therefore, we used a beta distribution with $\alpha = \beta = 1.2$ as the prior PDF on the independent parameters, transformed such that the probability is null outside the chosen range,
%
\begin{equation}
    p(\boldsymbol{\theta}_i) \propto \prod_{k=1}^{N_{\theta}} \mathcal{B}\left(\tilde{\theta}_{k, i} | 1.2, 1.2\right),
\end{equation}
%
where the beta distribution is defined as,
%
\begin{equation}
    \mathcal{B}(x | \alpha, \beta) = \frac{x^{\,\alpha-1}(1-x)^{\,\beta-1}}{\int_{0}^{1} u^{\,\alpha-1}(1-u)^{\,\beta-1} \mathrm{d} u}.
\end{equation}
%
and,
\begin{equation}
    \tilde{\theta}_{k, i} = \frac{\theta_{k, i} - \theta_{k, \mathrm{min}}}{\theta_{k, \mathrm{max}} - \theta_{k, \mathrm{min}}},
\end{equation}
is the transformed parameter where $\theta_{k, \mathrm{min}}$ and $\theta_{k, \mathrm{max}}$ are the upper and lower bounds for each parameter. The beta distribution was preferred over a bounded uniform distribution because our sampler evaluates the gradient of the posterior and is thus sensitive to discontinuities.

Using notation which represents a given random variable $x \sim q$ as equivalent to being drawn from a probability distribution $p(x) \propto q(x)$ where $q(x)$ is a non-normalised probability density function, we may write the priors for $\boldsymbol{\theta}_i$ as,
%
\begin{align*}
    f_{\mathrm{evol}, i} &\sim 0.01 + 1.99 \cdot \mathcal{B}(1.2, 1.2),\\
    M_i &\sim 0.8 + 0.4 \cdot \mathcal{B}(1.2, 1.2),\\
    \alpha_{\mathrm{MLT}, i} &\sim 1.5 + \mathcal{B}(1.2, 1.2),\\
    Y_{\mathrm{init}, i} &\sim 0.24 + 0.08 \cdot \mathcal{B}(1.2, 1.2),\\
    Z_{\mathrm{init}, i} &\sim 0.005 + 0.035 \cdot \mathcal{B}(1.2, 1.2),\\
\end{align*}
%
where each beta distribution is scaled to cover the boundaries of the grid of stellar models computed in Section \ref{sec:grid}.

We made predictions for each star using the trained ANN, $\{\log(\tau)_i, T_{\mathrm{eff}, i}, R_i, \dnu_i, \metallicity_{\mathrm{surf}, i}\} = \boldsymbol{f}_{\mathrm{ANN}}(\boldsymbol{\theta}_i)$, from which we derived the luminosity, $L_i$ using the Stefan-Boltzmann law. Out of the model parameters, those which may be observed are denoted by ${\boldsymbol{\mu}}_{i} = {\boldsymbol{f}}(\boldsymbol{\theta}_i)$. Therefore, we write the likelihood that we observe any $\boldsymbol{d}_i$ with known uncertainty, $\boldsymbol{\sigma}_{i}$ given our model as,
%
\begin{equation}
    p(\boldsymbol{d}_i | \boldsymbol{\theta}_i) = \prod_{k=1}^{N_\mathrm{obs}} \frac{1}{\sigma_{k, i} \sqrt{2\pi}} \exp\left[ - \frac{(d_{k, i} - \mu_{k, i})^2}{2 \sigma_{k, i}^2} \right],
    \label{eq:like}
\end{equation}
%
where $N_\mathrm{obs}$ is the number of observed variables. We chose to use observed $\teff$, $L$, $\dnu$ and $\metallicity$ collated for our sample as described in Section \ref{sec:data}.

@@

Similarly, for the second component of Equation \ref{eq:ppool}, we chose to partially-pool $\mlt$. We assume that convection in stars of a similar mass, evolutionary stage and area of the HR diagram may be approximated using a similar value of $\mlt$, but the accuracy of the mixing-length theory may vary from star-to-star. There is theoretical evidence for such a variation with $\metallicity$, $\teff$ and $\log{g}$ in 3D hydrodynamical stellar models \citep{Magic.Weiss.ea2015,Viani.Basu.ea2018}. However, investigating such dependencies are beyond this scope of this paper. Given the small range of our sample, any such variation will be absorbed by the spread parameter, $\sigma_\alpha$. Therefore, we decided to describe the prior on $\boldsymbol{\alpha}_\mathrm{MLT}$ as,
%
\begin{equation}
    p(\boldsymbol{\alpha}_{\mathrm{MLT}} | \mu_\alpha, \sigma_\alpha) = \prod_{i=1}^{N_\mathrm{stars}} \mathcal{N}({\alpha}_{\mathrm{MLT}, i} | \mu_\alpha, \sigma_\alpha)
\end{equation}
%

@@

We built another hierarchical model similar to the PP model except that $\mlt$ is max-pooled (MP). In this model, we assumed that $\mlt$ must be the same value for every star in the sample, but still allowed it to freely vary on a population-level. Thus the hyperparameters are now, $\boldsymbol{\phi} = \{\Delta Y/\Delta Z, Y_P, \sigma_Y, \mlt\}$. The posterior distribution of the model takes the same form as in Equation \ref{eq:hbmbayes} except that the mixing-length theory parameter for the $i$-th star is,
%
\begin{equation}
    \alpha_{\mathrm{MLT}, i} = \mlt,
\end{equation}
%
where,
\begin{equation}
    \mlt \sim 1.5 + \mathcal{B}(1.2, 1.2).
\end{equation}
% %
% \begin{equation}
%     p(\boldsymbol{\alpha}_\mathrm{MLT} | \mlt) = \prod_{i=1}^{N_\mathrm{stars}} \delta (\alpha_{\mathrm{MLT}, i} | \mlt)
% \end{equation}
% %
% where $\delta(x | \alpha)$ is defined as,
% %
% \begin{equation}
%     \delta(x | \alpha) = \begin{cases}
%         + \infty, &\quad x = \alpha\\
%         0, &\quad x \neq \alpha
%     \end{cases}
% \end{equation}
chosen such that $\mlt$ is confined to the boundaries of the grid of stellar models ($1.5 < \mlt < 2.5$).

@@

In this section, we present the results for each of the NP, PP and MP models with the sample of 81 APOKASC dwarfs and subgiants as inputs. We also present the results for the PPS and MPS models which include the Sun as a star in the population. Firstly, we show the reduction in age, mass and radius uncertainty with the addition of pooling in Section \ref{sec:param-results}. We then show the results for model hyperparameters in Section \ref{sec:hparam-results} where we infer the initial helium abundance and mixing-length parameter distribution in the sample.

@@

\section{Training the ANN}\label{sec:apx-train}
